---
title: "Info 498 Survey Results"
output: html_document
---

```{r, echo = FALSE, warning = FALSE, message = FALSE}
# Load various libraries
library(dplyr)
library(plotly)

# Read in .csv file with survey data
data <- read.csv("https://raw.githubusercontent.com/INFO-498F/a7-survey-data/master/intro_survey_data.csv")

# Set working directory so source() works correctly
setwd("/Users/planktonpey/Desktop/info498f/a7-collab")

# Read in summary functions
source("scripts/a7_summary_information.R")
summary_data <- simple_info(data)
```

`r summary_data$Number_of_Participants` Info 498 students responded to a variety of survey questions. A large majority of the class, `r summary_data$No_R_Experience` students, have never used the R programming language. Just under half of the students surveyed, `r summary_data$Uses_a_Mac` students to be exact, typically use a Mac, while a majority of `r summary_data$Interested_in_Informatics` students are interested in applying to the Informatics major. On a less technical note, of these students, `r summary_data$Hardcore_Seahawks_Fans` consider themselves to be hardcore Seahawks fans and `r summary_data$Likes_Just_Dogs` students are dog people. 

The chart below shows the varied experience Info 498 students have had with the R programming language.

```{r, echo = FALSE}
# Read in chart1 function and render chart
source("scripts/build_chart1.R")
build_chart1(data)
```

The chart below compares what operating system students use to past experience with the R programming language.

```{r, echo = FALSE}

# Read in chart2 function and render chart
source("scripts/build_chart2.r")
build_chart2(data)
```
